---
title: "Postcode Data Summary Statistics"
date: "10/02/2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(knitr)
source("postcode-data-summary-statistics.R")
```

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
  $(document).ready(function() {
    $("table").DataTable();
  } );
</script>

## Table of Changed Values Only

```{r echo = FALSE, result = "asis"}
df_diff %>% kable()
```

### Comments

There are ``r df_diff[[1]] %>% length()`` changed values.

There are ``r data_sets[[1]]$data$pivot_long[[3]] %>% unique() %>% length()`` unique values in data set one, and ``r data_sets[[2]]$data$pivot_long[[3]] %>% unique() %>% length()`` unique values in data set two.

There have been no values that have become `NA` or have changed data type.

## Note

If there are any statistics you would like, it won't take long to derive them from this point on.

## Complete Table of Comparisons

```{r}
df_join %>% kable()
```
